---
title: "K_Garcia_Part4RNotebook"
output:
  html_document:
    df_print: paged
---

Here I will create the logit model regression for my model
```{r}
#necessary packages
library(dplyr)
library(ggplot2)
library(stargazer)
library(tibble)
library(stringr)
library(tidyverse)
```

Importing the data into R, if cleaned in python.
```{r}
#First, I will import the csv file.
#Then, I will set the working directory and see all the column names in my file. 

#Setting the working directory
setwd("/Users/kgarcia/Documents/Spring '24/ECO590/Assignments/assn-3-regressions-KGARCIAAA")
nycvenues_raw <- read.csv('final_dataset.csv',header=T,na.strings=c(""))

names(nycvenues_raw) #allows me to see all the column names

#the second part of the read.csv changes all missing values in the data as NA
```

```{r}
#Checking for missing values and look at the number of unique values there are in each variable using sapply()

sapply(nycvenues_raw,function(x) sum(is.na(x)))
```
```{r}
#how many rows does each column have
sapply(nycvenues_raw, function(x) length(unique(x)))
```
```{r}
fivenum(nycvenues_raw$congestion_surcharge)
```

```{r}
#I want to know how service zone is being read by r, and whether it is reading it as a factor
is.factor(nycvenues_raw$service_zone)
```

```{r}
#Since it is not reading it as a factor

nycvenues_raw$service_zone <- factor(nycvenues_raw$service_zone)
nycvenues_raw$name <- factor(nycvenues_raw$name)

#Now I use the function contrast to make sure R knows that service zone & name are binary
contrasts(nycvenues_raw$service_zone)
contrasts(nycvenues_raw$name)
```
```{r}
# Converting service_zone into numeric new column to binary numbers
nycvenues_raw$service_zone_binary <- as.numeric(ifelse(nycvenues_raw$service_zone == "service_zone", 1, 0))

```

```{r}
nycvenues_raw$service_zone_binary <- as.numeric(nycvenues_raw$service_zone == "Yellow Zone")
```

Running an OLS model
```{r}
#Run a regression with OLS. Ensure that you have more than 3 variables. 

ols <- lm(num_rides_per_hour ~ trip_distance + total_plus_surcharge + total_amount + congestion_surcharge + VendorID, data = nycvenues_raw)

#Summary of the OLS regression model
summary(ols)
```

Running a regression with a filtered dataset:
```{r}
# First I will filter my data set for a specific venue
filtered_nycvenues <- nycvenues_raw %>% filter(service_zone == "Yellow Zone")

# Run a regression with the filtered data set
results2 <- lm(total_amount~ fare_amount, data = filtered_nycvenues)

# Print the summary of the regression model
summary(results2)

```

Running a preferred regressiong using my dataset:
```{r}
logit_model <- glm(service_zone_binary ~ num_rides_per_hour + total_plus_surcharge, data=nycvenues_raw, family=binomial)
summary(logit_model)
```

```{r}
logit_model2 <- glm(service_zone_binary ~ num_rides_per_hour + trip_distance, data=nycvenues_raw, family=binomial)
summary(logit_model2)
```

```{r}
#model3 <- glm(service_zone ~ num_rides_per_hour + pickup_hour, data=nycvenues_raw, family=binomial)
#takes too long because of the 'pickup hour'
```

Finding the marginal effect for model2
```{r}
#Marginal gives us the 'average' marginal effect for each variable
#install.packages("Margins")
library(margins)
```
```{r}
logit_m <- margins(logit_model2)
plot(logit_m)
```

```{r}
# 'trip_distance' is in miles
# the mean trip distance
mean_trip_distance <- mean(nycvenues_raw$trip_distance)

# the average marginal effect of trip distance for every 5 miles
marginal_effects <- margins(logit_model2, variables = "trip_distance", 
                             at = list(trip_distance = seq(0, 100, by = 5)))

summary(marginal_effects)

```

```{r}
# the mean number of rides per hour
mean_num_rides_per_hour <- mean(nycvenues_raw$num_rides_per_hour)

# the average marginal effect of num_rides_per_hour
marginal_effects2 <- margins(logit_model, variables = "num_rides_per_hour", 
                             at = list(num_rides_per_hour = mean_num_rides_per_hour))

summary(marginal_effects2)

```

```{r}
logit_model3 <- glm(service_zone_binary ~ num_rides_per_hour + trip_distance + total_amount + congestion_surcharge + total_plus_surcharge, data=nycvenues_raw, family=binomial)
summary(logit_model3)
```
```{r}
 # the mean trip distance
mean_trip_distance <- mean(nycvenues_raw$trip_distance)

# the average marginal effect of trip_distance
marginal_effects3 <- margins(logit_model3, variables = "trip_distance", 
                             at = list(trip_distance = mean_trip_distance))

summary(marginal_effects3)

```

```{r}
knitr::opts_chunk$set(echo = FALSE)
library(stargazer)
```

```{r}
stargazer(logit_model3,marginal_effects3, type = "text", 
          title = "Regression Model Results",
          covariate.labels = c("Number of Rides per hour", "Trip Distance (in Miles)", "Total Plus Surcharge", "Total Amount", "Congestion Surcharge", "Vendor ID"),
          dep.var.caption = "",
          dep.var.labels = "Service Zone",
          dep.var.labels.include = TRUE,
          notes.align = "l")
```

What does the regression tell us?

In a logistic regression model, the coefficients indicate the change in the log odds of the dependent variable (Service Zone) for a one unit change in the independent variable, holding all other variables constant. 

For the number of rides per hour, a one unit increase is associated with an increase in the log odds of service zone being a yellow zone by 1.337 units. 

For trip distance in miles, a one unit increase is associated with an increase in the log odds of the service zone being a yellow zone by 0.012 units. Although not statistically significant.

For Total plus surcharge, a one unit increase is associated with a decrease in the log odds of service zone being a yellow zone by 0.034 units. This is statistically significant at the 1% level.

For total amount, a one unit increase is associated with an increase in the log odds of service zone being a yellow zone by 0.515 units. Not statistically significant.

The coefficients for congestion surcharge and vendorID are not provided.

Overall, the model does not suggest strong evidence for the impact of these variables on the probability of the service zone being yellow (1) or boro zone (0), except for total plus surcharge, which was statistically significant. 

